State of the Art in Scientific Workflow Systems

### 2014-05-27 paper.tex
pegasus desc

%
\paragraph{Pegasus/DAX} Pegasus \cite{deelman-peg} is an SWE that is well-suited
to generate and execute large abstract DAGs made up of tasks with dataflow.
Abstract description is in the form of a DAG via a language called DAX. The
concrete expression takes into account the properties of application task
requirements and underlying compute resources. A Pegasus workflow is expressed
in a simple XML-based language called DAX (DAG in XML). DAX describes the
logical workflow components, their inputs and outputs and their links and
dependencies in a Pegasus workflow. These kind of workflows has been shown to
enact optimally using Pegasus' smart memory and disk management techniques.
Large scale workflows from astronomy, biology, and high-energy physics have
been shown to run via Pegasus on distributed computing resources such as
clusters, Grids and supercomputers. Pegasus manager buffers and maintains a
fix-sized window of executable tasks before accepting new tasks.  Regarding
massively parallel task scheduling, Pegasus provides a task
clustering technique that groups parallel jobs based on fixed parameters such
as number of groups. Recent developments in Pegasus enables it to run workflows
on cloud environments~\cite{peg-cloud}.

>>>>

%
\paragraph{Pegasus/DAX} Pegasus \cite{deelman-peg} is an SWE that is
well-suited to generate and execute large workflows from abstract DAGs
describing dataflow.  Abstract description of a DAG is done via an XML-based
language called DAX. The concrete expression takes into account the properties
of application task requirements and underlying distributed compute resources.
The main advantage of such approach is that a single abstract workflow
description can be mapped to multiple execution environments based on
requirements. DAX describes the logical workflow components, their inputs and
outputs and their links and dependencies in a Pegasus workflow. These kind of
workflows have been shown to enact optimally using Pegasus' dynamic task,
memory and disk management techniques. For instance, for massively parallel
task scheduling, Pegasus provides a task clustering technique that groups
parallel jobs based on fixed parameters such as number of groups. Additionally,
a manager buffers and maintains a fix-sized window of executable tasks before
accepting new tasks.

Large scale workflows from astronomy, biology, and high-energy physics have
been shown to run via Pegasus on distributed computing resources such as
clusters, Grids and supercomputers.  Recent developments in Pegasus enables it
to run workflows on cloud environments~\cite{peg-cloud}. Pegasus system is
known to be extendible as illustrated by a recent integration
effort~\cite{peg-hubzero} between Pegasus and the Hubzero
portal~\cite{hubzero}.
